Nilpotent Invariants \\ for Generic Discrete Series of Real Groups

### 2025-12-15 revision_whittaker.tex
Adds revision file

Let us now explain the strategy of the proof, which is mainly an exercise in putting together some references that are rather scattered in the literature. What we shall actually do is: introduce a finite group~$Q(G)$, and point out that 
\begin{itemize}
\item[(i)] it acts transitively on~(1), and simply transitively on (2)--(4);
\item[(ii)] the maps $\pi \mapsto \Wh(\pi)$, $\pi \mapsto \AV(\pi)$ and $\pi\mapsto \WF(\pi)$  are equivariant for these actions.
\end{itemize}
The theorem follows immediately from these two observations, and from the following basic fact on group actions.

@@

@@

>>>>

Let us now explain the strategy of the proof, which is mainly an exercise in putting together some references that are rather scattered in the literature. What we shall actually do is: introduce a finite group~$Q(G)$, and point out that 
\begin{itemize}
\item[(i)] it acts transitively on~(1), and simply transitively on (2)--(4);
\item[(ii)] the maps $\pi \mapsto \Wh(\pi)$, $\pi \mapsto \AV(\pi)$ and $\pi\mapsto \WF(\pi)$  are equivariant for these actions.
\end{itemize}
The theorem follows immediately from these two observations, and from the following basic fact on group actions, whose proof is left to the reader.

@@

\begin{center} \textcolor{red}{TODO : indicate in which sections of the paper we prove each of the statements in (i)-(ii) about the actions of $Q(G)$. }\end{center}

\begin{remark} \textcolor{red}{\textup{TODO : add a remark about the case of fundamental series packets, in case there is no DS. }}\end{remark}

\begin{remark} \textcolor{red}{\textup{TODO : say what this looks like when $G$ is adjoint, or simply connected, and add a remark on the general case.}  }\end{remark}

@@

\begin{center} \textcolor{red}{TO DO : explain that this preserves generic representations, and  DS representations within a single $L$-packet.\\ Then explain why the action is transitive.   }\end{center}
